Risk Perceptions for Wearable Devices

### 2015-03-05 tex-inputs/appendixes.tex
cleanup
sprinkled things to talk about inline
made it so every tex input file can compile the paper
Added full regression model to Appendix
Added more models to appendices

\appendix
\section{Fischhoff Prompts}
\label{sec:prompt}

@@

%\section{Risk and Benefit Rankings}
%\label{sec:techrank}
%
%BENEFIT: 
%
%technology 	median	25\%		75\% \\
%electricity	87	50	100\\
%internet	65	45	100\\
%laptops	60	40	80\\
%email	50	30	75\\
%smartphones	50	32.5	75\\
%location tracking	40	20	67.5\\
%heart rate detection	40	28	62.5\\
%language detection	35	15	60\\
%voice recognition	25	15	40\\
%speech to text	25	15	36.25\\
%lawnmowers	24	15	40\\
%facial recognition	22	13	40\\
%guns	20	10	30\\
%motrocycles	20	12	40\\
%voice based emotion detection	20	10	30\\
%facial detection	20	10	32\\
%discrete camera	20	15	30\\
%smartwatches	20	10	32.5\\
%google glass	20	12	40\\
%fitness trackers	19	10	30\\
%cubetastic	18	10	30\\
%discrete microphone	15	10	20\\
%age detection	12	10	21\\
%gender detection	10	10	15
%
%RISK: 
%
%technology 	median	25\%		75\%\\
%guns	60	40	80\\
%motrocycles	45	27	70\\
%electricity	25	15	40\\
%lawnmowers	20	12	30\\
%facial recognition	17	12.5	30\\
%internet	15	10	30\\
%discrete camera	12	10	30\\
%location tracking	10	10	20\\
%age detection	10	10	15\\
%gender detection	10	10	12\\
%language detection	10	10	10\\
%voice based emotion detection	10	10	15\\
%facial detection	10	10	25\\
%voice recognition	10	10	15\\
%heart rate detection	10	10	10\\
%email	10	10	16\\
%speech to text	10	10	10\\
%discrete microphone	10	10	20\\
%smartphones	10	10	19\\
%laptops	10	10	15\\
%fitness trackers	10	10	10\\
%smartwatches	10	10	10\\
%google glass	10	10	20\\
%cubetastic	10	10	30

@@

>>>>

%!TEX root = ../paper.tex
\appendix

\section{Fischhoff Prompts}
\label{sec:prompt}

@@

@@

\onecolumn
\section{Full Regression Model from Data Types}
\label{sec:regression}
%\begin{figure*}[t]
\includegraphics[page=1,scale=0.8]{images/full-model.pdf}
\includepdf[pages=2-3,scale=0.8]{images/full-model.pdf}

%\caption{Full regression model, which includes all 72 data types, recipients, and covariates.}
%\end{figure*}

\section{Full Regression Model from Data Risks / Data Categories}
\label{sec:regression}
%\begin{figure*}[t]
\includegraphics[page=1,scale=0.8]{images/full-model2.pdf}
\includepdf[pages=2,scale=0.8]{images/full-model2.pdf}

\twocolumn

### 2015-03-05 tex-inputs/results-regression.tex
Added more models to appendices

We created several models using two independent variables as predictors: data recipient and data type. Because the device type independent variable (i.e., whether they were using the Cubetastic3000 or a smartphone) was only varied for the 5 smartphone misbehaviors listed in Section \ref{sec:smartphones}, we removed these 5 data types from our models, which resulted in a total of 72 data types shared between 4 possible recipients. We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score. For each model, we performed Wald's test to examine the model effects attributable to each of these parameters and observed that the only covariates that had an observable effect on our models were gender and participants' IUIPC scores, which also exhibited an interaction effect with each other. Thus, we opted to remove the other covariates from our analysis. Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit). As can be seen, the data type was the strongest predictor of VUR.

@@

\begin{table}[t]
\centering
\begin{tabular}{|l| r| r| r|}
\hline
Parameters & $\chi^2$ & $df$ & QIC\\
\hline
\hline
(Intercept) & 442.66 & 1 & 12,727.42\\
Risk & 405.18 & 4 & \\
\hline
(Intercept) & 380.39 & 1 & 12,681.86\\
Capture & 439.45 & 5 & \\
\hline
(Intercept) & 256.15 & 1 & 12,061.87\\
Risk & 157.84 & 4 & \\
Medium & 183.90 & 5 & \\
Risk $\times$ Medium & 259.81 & 8 & \\
\hline
(Intercept) & 62.65 & 1 & 10,406.35\\
Risk & 205.21 & 4 & \\
Medium & 250.35 & 5 & \\
Recipient & 546.89 & 3 & \\
IUIPC (covariate) & 103.94 & 1 & \\
Gender (covariate) & 9.80 & 1 & \\
IUIPC $\times$ Gender & 8.21 & 1 & \\
Risk $\times$ Medium & 303.44 & 8 & \\
Recipient $\times$ Risk & 39.14 & 12 & \\
\hline
\end{tabular}
\caption{Goodness-of-fit metrics for additional binary logistic models of our data using general estimating equations to account for repeated measures. The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model. Each parameter listed was statistically significant at $p<0.005$.}
\label{regression2}
\end{table}

>>>>

We created several models using two independent variables as predictors: data recipient and data type. Because the device type independent variable (i.e., whether they were using the Cubetastic3000 or a smartphone) was only varied for the 5 smartphone misbehaviors listed in Section \ref{sec:smartphones}, we removed these 5 data types from our models, which resulted in a total of 72 data types shared between 4 possible recipients. We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score. For each model, we performed Wald's test to examine the model effects attributable to each of these parameters and observed that the only covariates that had an observable effect on our models were gender and participants' IUIPC scores, which also exhibited an interaction effect with each other. Thus, we opted to remove the other covariates from our analysis. Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit). As can be seen, the data type was the strongest predictor of VUR. The coefficients for the model with the best fit can be seen in Appendix \ref{sec:regression}.

@@

\begin{table}[t]
\centering
\begin{tabular}{|l| r| r| r|}
\hline
Parameters & $\chi^2$ & $df$ & QIC\\
\hline
\hline
(Intercept) & 442.66 & 1 & 12,727.42\\
Risk & 405.18 & 4 & \\
\hline
(Intercept) & 380.39 & 1 & 12,681.86\\
Data Category & 439.45 & 5 & \\
\hline
(Intercept) & 256.15 & 1 & 12,061.87\\
Risk & 157.84 & 4 & \\
Data Category & 183.90 & 5 & \\
Risk $\times$ Data Category & 259.81 & 8 & \\
\hline
(Intercept) & 62.65 & 1 & 10,406.35\\
Risk & 205.21 & 4 & \\
Data Category & 250.35 & 5 & \\
Recipient & 546.89 & 3 & \\
IUIPC (covariate) & 103.94 & 1 & \\
Gender (covariate) & 9.80 & 1 & \\
IUIPC $\times$ Gender & 8.21 & 1 & \\
Risk $\times$ Data Category & 303.44 & 8 & \\
Recipient $\times$ Risk & 39.14 & 12 & \\
\hline
\end{tabular}
\caption{Goodness-of-fit metrics for additional binary logistic models of our data using general estimating equations to account for repeated measures. The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model. Each parameter listed was statistically significant at $p<0.005$.}
\label{regression2}
\end{table}
